Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex

\subsubsection{Server Application Programming Interface}
The {\em Server Application Programming Interface} is what connects the {\em Game} to our central recording server. Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present. A unique identifier is computed and stored by the Kimbee System that will uniquely identify recordings in the central server as belonging to a particular child's device. This unique identifier is accessible via the Options Screen in the {\em Phaser Game Implementation}.

@@

\subsubsection{Therapist Portal Application Programming Interface}
  The server exposes a set of APIs for the {\em Therapist Portal} to utilize. This includes functionality to retrieve recordings for a particular child owned by the therapist record, retrieve the authenticated therapist record, authenticate therapists, and register therapists. This functionality is used via a HTTP interface with the {\em Central Server}.

>>>>

\subsubsection{Server API}
The {\em Server API} is what connects the {\em Game} to our central recording server. Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present. A unique identifier is computed and stored by the Kimbee System that will uniquely identify recordings in the central server as belonging to a particular child's device. This unique identifier is accessible via the Options Screen in the {\em Phaser Game Implementation}.

@@

\subsubsection{Therapist Portal API}
  The server exposes a set of APIs for the {\em Therapist Portal} to utilize. This includes functionality to retrieve recordings for a particular child owned by the therapist record, retrieve the authenticated therapist record, authenticate therapists, and register therapists. This functionality is used via a HTTP interface with the {\em Central Server}.
